### 2017-01-25 manuscript.rmd
author name changed
typos

Casey W. Dunn^1^*, Felipe Zapata^1,2^, Cat Munro^1^, Stefan Siebert^1,3^, Andreas Hejnol^4^

@@

The focus of genomics research has quickly shifted from describing genome sequences to functional genomics, the study of how genomes "work" using tools that measure functional attributes such as expression, chromatin state, and transcription initiation. functional genomics, in turn, is now becoming more comparative- there is great interest in understanding how functional genomic variation across species gives rise to a diversity of development, morphology, physiology, and other phenotypes [@Wray:2013gh]. Comparative Functional Genomics (CFG) analyses are also critical to transferring functional insight across species, and will grow in importance in coming years.

@@

Despite its importance, there have been relatively few tests of the ortholog conjecture. Previous work has shown that ontology annotations are not sufficient to test the ortholog conjecture [@Chen:2012jz; @Thomas:2012hz]. Analyses of domain structure were consistent with ortholog conjecture [@Forslund:2011cw]. There have been few tests of the ortholog conjecture with regards to gene expression [@Chen:2012jz], and KMRR is the most thorough such expression study to date.

>>>>

Casey W. Dunn^1^*, Felipe Zapata^1,2^, Catriona Munro^1^, Stefan Siebert^1,3^, Andreas Hejnol^4^

@@

The focus of genomics research has quickly shifted from describing genome sequences to functional genomics, the study of how genomes "work" using tools that measure functional attributes such as expression, chromatin state, and transcription initiation. Functional genomics, in turn, is now becoming more comparative- there is great interest in understanding how functional genomic variation across species gives rise to a diversity of development, morphology, physiology, and other phenotypes [@Wray:2013gh]. Comparative Functional Genomics (CFG) analyses are also critical to transferring functional insight across species, and will grow in importance in coming years.

@@

Despite its importance, there have been relatively few tests of the ortholog conjecture. Previous work has shown that ontology annotations are not sufficient to test the ortholog conjecture [@Chen:2012jz; @Thomas:2012hz]. Analyses of domain structure were consistent with the ortholog conjecture [@Forslund:2011cw]. There have been few tests of the ortholog conjecture with regards to gene expression [@Chen:2012jz], and KMRR is the most thorough such expression study to date.
